Hybrid Recurrent Model With External Weak Signals

### 2021-08-08 hybridmodel.tex
Discussion on the choice of model/loss function
A few corrections

Consider $N\geqslant 1$ time series. For all $1\leqslant n \leqslant N$ and $1\leqslant t \leqslant T$, let $\ts_t^n$ be the value of the $n$-th sequence at time $t$ and  $\fullts^n = \{\ts_t^n\}_{1\leqslant t \leqslant T}$ be all the values of this sequence.   The objective of this paper is to propose a model to  forecast all time series in a given time frame  $\lag \in \mathbb{N}$, i.e. we aim at sampling $\{\ts^n_{t+1:t+\lag}\}_{1\leqslant n \leqslant N}$ based on $\{\ts^n_{1:t}\}_{1\leqslant n \leqslant N}$.

@@

\subsection{Per time series statistical model}
%The first step in our additive hybrid model is to consider, for each time series, an exponential smoothing  statistical model.
The time-series-specific models compute, for each sequence, two components,  level  and  seasonality. For all $1\leqslant n \leqslant N$ and $0\leqslant t \leqslant T$, let $\lvl_t^n$ be the value of the $n$-th level component at time $t$ and  $\fulllvl^n = \{\lvl_t^n\}_{0\leqslant t \leqslant T}$ be all the values of this level component. For all $1\leqslant n \leqslant N$ and $-m+1\leqslant t \leqslant T$, let $\seas_t^n$ be the value of the $n$-th seasonality component at time $t$ and  $\fullseas^n = \{\seas_t^n\}_{-m+1\leqslant t \leqslant T}$ be all the values of this season component. $m \in \mathbb{N}$ is the seasonality length (4 for quarterly, 12 for monthly or 52 for weekly time series). Given the sequence $\fullts^n$, the two components  $\fulllvl^n$ and $\fullseas^n$ are computed using exponential smoothing.
For all $1\leqslant n \leqslant N$, let $\Theta^n = \{\alpha^n, \gamma^n,\{\seas_t^n\}_{-m+1\leqslant t \leqslant 0}\}$ be the parameters of the $n$-th sequence with $\lsmooth^n$ and $\ssmooth^n$ the positive smoothing parameters and $\{\seas_t^n\}_{-m+1\leqslant t \leqslant 0}$ the $m$ first seasonality terms. We initialize the first level with $\lvl^n_{0} = \sum_{t = 1}^m \ts^n_{t}/m$ and, for all $1\leqslant n \leqslant N$ and $1\leqslant t \leqslant T$,
\begin{align*}
    \lvl^n_{t} &= \lsmooth^n (\ts^n_t - \seas^n_{t-m}) + (1- \lsmooth^n)\lvl^n_{t-1}\,, \\
    \seas^n_t &= \ssmooth^n (\ts^n_t - \lvl^n_{t-1}) + (1 - \ssmooth^n)\seas^n_{t-1}\,. 
\end{align*}

@@

Then we train a global RNN on all sequences to compute a correction of the first statistical prediction. We motivate this choice for two reasons. Firstly, pure machine learning methods achieve relatively poor results in time series forecasting. Turning a full forecasting task into a correcting task largely simplifies the RNN goals. Secondly, neural network needs a thorough data pre-processing and classical pre-processing methods are not really suited for time-series. With our collection of exponential smoothing models, we propose a fine way to normalize and deseasonalize the RNN inputs and outputs. %We describe bellow how we design a RNN able to understand the first exponential smoothing models and estimate a correction of their forecasting errors.

@@

>>>>

Consider $N\geqslant 1$ time series. For all $1\leqslant n \leqslant N$ and $1\leqslant t \leqslant T$, let $\ts_t^n$ be the value of the $n$-th sequence at time $t$ and  $\fullts^n = \{\ts_t^n\}_{1\leqslant t \leqslant T}$ be all the values of this sequence.   The objective of this paper is to propose a model to  forecast all time series in a given time frame  $\lag \in \mathbb{N}$, i.e. we aim at sampling $\{\ts^n_{T+1:T+\lag}\}_{1\leqslant n \leqslant N}$ based on $\{\ts^n_{1:T}\}_{1\leqslant n \leqslant N}$.

@@

\subsection{Per time series statistical model}
%The first step in our additive hybrid model is to consider, for each time series, an exponential smoothing  statistical model.
The time-series-specific models compute, for each sequence, two components,  level  and  seasonality. For all $1\leqslant n \leqslant N$ and $0\leqslant t \leqslant T$, let $\lvl_t^n$ be the value of the $n$-th level component at time $t$ and  $\fulllvl^n = \{\lvl_t^n\}_{0\leqslant t \leqslant T}$ be all the values of this level component. For all $1\leqslant n \leqslant N$ and $-m+1\leqslant t \leqslant T$, let $\seas_t^n$ be the value of the $n$-th seasonality component at time $t$ and  $\fullseas^n = \{\seas_t^n\}_{-m+1\leqslant t \leqslant T}$ be all the values of this season component. $m \in \mathbb{N}$ is the seasonality (4 for quarterly, 12 for monthly or 52 for weekly time series). Given the sequence $\fullts^n$, the two components  $\fulllvl^n$ and $\fullseas^n$ are computed using exponential smoothing.
For all $1\leqslant n \leqslant N$, let $\Theta^n = \{\alpha^n, \gamma^n,\{\seas_t^n\}_{-m+1\leqslant t \leqslant 0}\}$ be the parameters of the $n$-th sequence with $\lsmooth^n$ and $\ssmooth^n$ the positive smoothing parameters and $\{\seas_t^n\}_{-m+1\leqslant t \leqslant 0}$ the $m$ first seasonality terms. We initialize the first level with $\lvl^n_{0} = \sum_{t = 1}^m \ts^n_{t}/m$ \textcolor{red}{issue with the time index ?} and, for all $1\leqslant n \leqslant N$ and $1\leqslant t \leqslant T$,
\begin{align*}
    \lvl^n_{t} &= \lsmooth^n (\ts^n_t - \seas^n_{t-m}) + (1- \lsmooth^n)\lvl^n_{t-1}\,, \\
    \seas^n_t &= \ssmooth^n (\ts^n_t - \lvl^n_{t-1}) + (1 - \ssmooth^n)\seas^n_{t-1}\,. 
\end{align*}

@@

Then, we train a global RNN on all sequences to compute a correction of the initial prediction. %We motivate this choice for two reasons. Firstly, pure machine learning methods achieve relatively poor results in time series forecasting. Turning a full forecasting task into a correcting task largely simplifies the RNN goals. 
This task requires a thorough data pre-processing and with our collection of exponential smoothing models  we propose a fine way to normalize and deseasonalize the RNN inputs and outputs. %We describe bellow how we design a RNN able to understand the first exponential smoothing models and estimate a correction of their forecasting errors.

@@

\subsection{Examples from the dataset}
\label{section:examples}
